---
title: "April 2025 New Data Import"
author: "Ben Szeto"
date: "2025-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r, libraries}

library(tidyverse)
library(ipumsr)
library(survey)
library(srvyr)
library(table1)
library(naniar)
```

```{r, importing data}
ddi <- read_ipums_ddi("C:/Users/bszet/Box/CARE Scholars 2024 - Diabetes Mortality Project/Data and Code/nhis_00029.xml")

data1 <- read_ipums_micro(ddi)

ddi <- read_ipums_ddi("C:/Users/bszet/Box/CARE Scholars 2024 - Diabetes Mortality Project/Data and Code/nhis_00027.xml")

data2 <- read_ipums_micro(ddi)

ddi <- read_ipums_ddi("C:/Users/bszet/Box/CARE Scholars 2024 - Diabetes Mortality Project/Data and Code/nhis_00030.xml")

data3 <- read_ipums_micro(ddi)


ddi <- read_ipums_ddi("C:/Users/bszet/Box/CARE Scholars 2024 - Diabetes Mortality Project/Data and Code/nhis_00001.xml") #Earnings Data

data4 <- read_ipums_micro(ddi)


```
```{r, merging data}
data1<-data1%>%#Selecting variables of interest from data1
  select(NHISPID, DIABETICAGE, DIAYRSAGO)

data3<-data3%>%#Selecting variables of interest from data3
  select(NHISPID, MORTDODY, MORTSTAT)

data4<-data4%>%#Selecting variables of interest from data1
  select(NHISPID, INCFAM97ON2, INCIMP1, INCIMP2, INCIMP3, INCIMP4, INCIMP5, IMPYFAMFLAG1, IMPYFAMFLAG2, IMPYFAMFLAG3,IMPYFAMFLAG4, IMPYFAMFLAG5, EARNIMP1, EARNIMP2, EARNIMP3, EARNIMP4, EARNIMP5 )


data<-merge(data1, data2, by="NHISPID")
data<-merge(data, data3, by="NHISPID")
data<-merge(data, data4, by="NHISPID")

data_prefilter<-data#Saving a copy so don't need to rerun code all the time
```

```{r, data cleaning}
#Refactoring
data<-data%>%
  mutate(Race=as_factor(RACEA))%>%#RACEA to Race
  mutate(mortstat=as_factor(MORTSTAT))%>%
  mutate(morthypr=as_factor(MORTHYPR))%>%
  mutate(sex=as_factor(SEX))


#Filtering
data<-data%>%
  filter(Race%in%c("Chinese", "Asian Indian", "White", "Filipino"))%>% #selecting Chinese, Asian Indian, Filipino, and White
  #filter(!BMI==0)%>% #filtering out extraneous BMIs #see section below
  #filter(BMI<90)%>%
  filter(MORTELIG==1)%>%#Make sure part of mortality data set, People who are less than 18 are not eligible
  filter(!(HISPYN==2 & Race=="White"))#Removing NHW


#If want to keep missing BMI and set to missing
data<-data%>%
  mutate(BMI=ifelse(BMI==0|BMI>90, "MISSING", BMI))
```

```{r}

data<-data%>%
  mutate(BMI_R_Cat=ifelse(BMI=="MISSING", "MISSING",ifelse(Race=="White", #Creating BMI Categorizations
                          case_when(BMI<18.5~"Underweight",#BMI thresholds for Whites
                                    BMI>=18.5 & BMI<25~"Normal Weight",
                                    BMI>=25 & BMI <30~"Overweight",
                                    BMI>=30~"Obese"),
                          case_when(BMI<18.5~"Underweight",#BMI thresholds for Asians (Considered all races not White)
                                    BMI>=18.5 & BMI<23~"Normal Weight",
                                    BMI>=23 & BMI <27.5~"Overweight",
                                    BMI>=27.5~"Obese"))))%>%#27.5 is obese for Asians
  mutate(Education_recode=case_when(#Education recoding
    EDUCREC2%in%c(10,20,30,31,32,40,41)~"Did Not Complete High School",
    EDUCREC2==42~"High School Grad",
    EDUCREC2%in%c(50,51,52,53)~"Some College",
    EDUCREC2==54~"4 years college/Bachelor's degree",
    EDUCREC2==60~"Post Bachelor",
    EDUCREC2%in%c(96, 97,98,99)~"Unknown",
    EDUCREC2==0~"NIU", 
    TRUE~"Check Again"
  ))%>%
  mutate(Smoking_recode=case_when(
    SMOKESTATUS2%in%c(10,11,12,13)~"Current Smoker",
    SMOKESTATUS2%in%c(20,40)~"Former Smoker",
    SMOKESTATUS2%in%c(30)~"Never Smoked",
    SMOKESTATUS2==90~"Unknown",
    TRUE~"Unknown"#Check this code later
  ))%>%
  mutate(Insurance_Status=case_when(
    HINOTCOVE==1~"Covered",
    HINOTCOVE==2~"Uncovered",
    HINOTCOVE%in%c(7,8,9)~"Unknown",
    TRUE~"Check Code"
  ))%>%
  mutate(USBorn_Recode=case_when(
         USBORN%in%c(10,11,12)~"Born Outside US",
         USBORN==20~"Born in US",
         TRUE~"MISSING"))%>%
  # move to factoring part of code mutate(USBorn_Recode=relevel(droplevels(as_factor(USBorn_Recode)), "Born in US"))
  mutate(Earnings_recode=as_factor(case_when(
    EARNINGS%in%c(0,97,98,99)~"NIU/Unknown",
    EARNINGS%in%c(1,2,3,4,5,6)~"Low Income ($1-$34,999)",
    EARNINGS%in%c(7,8,9,10)~"Middle Income($35,000-$74,999)",
    EARNINGS==11~"High Income(>$75,000)"
  )))%>%
  # Move down to facotring part mutate(Earnings_recode=factor(Earnings_recode, levels=c("Low Income ($1-$34,999)", "Middle Income($35,000-$74,999)","High Income(>$75,000)","NIU/Unknown"  )))%>%
  mutate(Diabetes_Lifetime=case_when(
    DIABETICEV==2|MORTDIAB==2~"Diabetic",
    DIABETICEV%in%c(0,7,8,9) & MORTDIAB==9~"Unknown/Not in Universe",
    TRUE~"Non-Diabetic"
  ))%>%
  mutate(Mort_recode=ifelse(MORTSTAT==1, TRUE, FALSE))%>%
  mutate(Mortality_Status=ifelse(MORTSTAT==1, "Presummed Dead", "Presummed Alive"))%>%#manually making the interaction term
  mutate(Diabetes_Lifetime_Race=as_factor(ifelse(
    Diabetes_Lifetime=="Diabetic",
    case_when(
      Race=="White"~"White Diabetic",
      Race=="Asian Indian"~"Asian Indian Diabetic",
      Race=="Filipino" ~"Filipino Diabetic",
      Race=="Chinese"~"Chinese Diabetic",
      TRUE~"Check Code"),
    "Non-Diabetic"
  )))%>%
  mutate(HYPERTENEV_recode=case_when(#Go back and relevel for regression?
    HYPERTENEV==1~"No",
    HYPERTENEV==2~"Yes",
    HYPERTENEV%in%c(7,8,9)~"Unknown",
    TRUE~NA
  ))%>%
  mutate(exposure_birth=ifelse(
    MORTSTAT==1,
    MORTDODY-YEAR+AGE,#If dead, time ends at year of death
    2019-YEAR+AGE#If alive or NIU, time ends at 2019
    ))%>%
  mutate(Lifespan_Diabetic=ifelse(
    Diabetes_Lifetime=="Diabetic"&MORTSTAT==1,
    exposure_birth,
    NA
  ))%>%
  mutate(Age_Diabetes_Diagnosis=ifelse(DIABETICAGE==96, NA, DIABETICAGE))%>%
  mutate(Diabetes_Over_Race=as_factor(ifelse(
    Diabetes_Lifetime=="Diabetic",
    case_when(
      Race=="White"~"White Diabetic",
      Race=="Asian Indian"~"Asian Indian Diabetic",
      Race=="Filipino" ~"Filipino Diabetic",
      Race=="Chinese"~"Chinese Diabetic",
      TRUE~"Check Code"),
    case_when(
      Race=="White"~"White Non-diabetic",
      Race=="Asian Indian"~"Asian Indian Non-diabetic",
      Race=="Filipino" ~"Filipino Non-diabetic",
      Race=="Chinese"~"Chinese Non-diabetic",
      TRUE~"Check Code")
  )))

```

```{r, leveling}
data<-data%>%
  mutate(Race=factor(droplevels(Race), c("White", "Chinese", "Filipino", "Asian Indian")))%>%
  mutate(Education_recode=factor(Education_recode, levels=c("High School Grad", "Did Not Complete High School","Some College", "4 years college/Bachelor's degree", "Post Bachelor", "Unknown")))%>%
  mutate(Smoking_recode=factor(Smoking_recode, c("Never Smoked", "Current Smoker", "Former Smoker", "Unknown")))%>%
  mutate(Insurance_Status=factor(Insurance_Status, c("Covered", "Uncovered", "Unknown")))%>%
  mutate(Earnings_recode=factor(Earnings_recode, c("Middle Income($35,000-$74,999)","Low Income ($1-$34,999)","High Income(>$75,000)", "NIU/Unknown")))%>%
  mutate(sex=factor(droplevels(sex), c("Male", "Female")))%>%
  mutate(Diabetes_Lifetime_Race=factor(Diabetes_Lifetime_Race, c("Non-Diabetic","White Diabetic", "Chinese Diabetic", "Filipino Diabetic","Asian Indian Diabetic")))%>%
  mutate(Diabetes_Lifetime=factor(Diabetes_Lifetime, c("Non-Diabetic", "Diabetic")))%>%#Removing people who are unknown for diabetes or not
  mutate(Diabetes_Over_Race=factor(Diabetes_Over_Race, c("White Non-diabetic","Asian Indian Non-diabetic", "Filipino Non-diabetic", "Chinese Non-diabetic","White Diabetic",  "Asian Indian Diabetic", "Filipino Diabetic", "Chinese Diabetic" )))%>%
  mutate(BMI_R_Cat=factor(BMI_R_Cat, c("Normal Weight", "Underweight", "Overweight", "Obese", "MISSING")))
  
  

levels(data$Race)
levels(data$Education_recode)
levels(data$Smoking_recode)
levels(data$Insurance_Status)
```

```{r, filtering out those NIU diabetes}


data<-data%>%
  filter(!is.na(Diabetes_Lifetime))

```

```{, testing missingness}
unique(data$INCFAM97ON2)
  
table(data$INCFAM97ON2)


table(data$INCIMP2)
```

```{r}

colnames(data)

```
Jump to Variable
YEAR (Survey year)
SERIAL (Sequential Serial Number, Household Record)
STRATA (Stratum for variance estimation)
PSU (Primary sampling unit (PSU) for variance estimation)
NHISHID (NHIS Unique identifier, household)
HHWEIGHT (Household weight, final annual)
PERNUM (Person number within family/household (from reformatting))
NHISPID (NHIS Unique Identifier, person)
HHX (Household number (from NHIS))
FMX (Family number (from NHIS))
PX (Person number of respondent (from NHIS).)
PERWEIGHT (Final basic annual weight)
SAMPWEIGHT (Sample Person Weight)
FWEIGHT (Final annual family weight)
ASTATFLG (Sample adult flag)
CSTATFLG (Sample child flag)
INCFAM97ON2 (Total combined family income (1997+ w. 2007 categories))
INCIMP1 (Imputed total combined family income (1997+ grouping))
INCIMP2 (Imputed total combined family income (1997+ grouping))
INCIMP3 (Imputed total combined family income (1997+ grouping))
INCIMP4 (Imputed total combined family income (1997+ grouping))
INCIMP5 (Imputed total combined family income (1997+ grouping))
IMPYFAMFLAG1 (Family income group imputation flag 1)
IMPYFAMFLAG2 (Family income group imputation flag 2)
IMPYFAMFLAG3 (Family income group imputation flag 3)
IMPYFAMFLAG4 (Family income group imputation flag 4)
IMPYFAMFLAG5 (Family income group imputation flag 5)
EARNINGS (Person's total earnings, previous calendar year)
EARNIMP1 (Person's imputed total earnings, previous calendar year)
EARNIMP2 (Person's imputed total earnings, previous calendar year)
EARNIMP3 (Person's imputed total earnings, previous calendar year)
EARNIMP4 (Person's imputed total earnings, previous calendar year)
EARNIMP5 (Person's imputed total earnings, previous calendar year)

```{r}
#missingness_test_set<-data%>%#Selecting variables of interest from data1
 # select(NHISPID, ASTATFLG, CSTATFLG, INCFAM97ON2, INCIMP1, INCIMP2, INCIMP3, INCIMP4, INCIMP5, IMPYFAMFLAG1, IMPYFAMFLAG2, IMPYFAMFLAG3,IMPYFAMFLAG4, IMPYFAMFLAG5, EARNINGS, EARNIMP1, EARNIMP2, EARNIMP3, EARNIMP4, EARNIMP5 )

missingness_test_set<-data%>%
  select(INCFAM97ON2,#Total combined family income (1997+ w. 2007 categories
         INCIMP1, #(Imputed total combined family income (1997+ grouping))
         INCIMP2, #(Imputed total combined family income (1997+ grouping))
         INCIMP3, #(Imputed total combined family income (1997+ grouping))
         INCIMP4, #(Imputed total combined family income (1997+ grouping))
         INCIMP5, #(Imputed total combined family income (1997+ grouping)))
         IMPYFAMFLAG1, #(Family income group imputation flag 1)
         IMPYFAMFLAG2, #(Family income group imputation flag 2)
         IMPYFAMFLAG3, #(Family income group imputation flag 3)
         IMPYFAMFLAG4, #(Family income group imputation flag 4)
         IMPYFAMFLAG5, #(Family income group imputation flag 5)
         EARNINGS, #(Person's total earnings, previous calendar year)
         EARNIMP1, #(Person's imputed total earnings, previous calendar year)
         EARNIMP2, #(Person's imputed total earnings, previous calendar year)
         EARNIMP3, #(Person's imputed total earnings, previous calendar year)
         EARNIMP4, #(Person's imputed total earnings, previous calendar year)
         EARNIMP5 #(Person's imputed total earnings, previous calendar year)
  )




lapply(missingness_test_set, unique)

missingness_test_set2<-missingness_test_set%>%
  mutate(INCFAM97ON2=ifelse(INCFAM97ON2%in%c(97:99), NA, INCFAM97ON2))%>%
  mutate( EARNINGS=ifelse(EARNINGS==0, NA,  EARNINGS))%>%
  mutate( EARNIMP1=ifelse(EARNIMP1==0, NA,  EARNIMP1))%>%
  mutate( EARNIMP2=ifelse(EARNIMP2==0, NA,  EARNIMP2))%>%
  mutate( EARNIMP3=ifelse(EARNIMP3==0, NA,  EARNIMP3))%>%
  mutate( EARNIMP4=ifelse(EARNIMP4==0, NA,  EARNIMP4))%>%
  mutate( EARNIMP5=ifelse(EARNIMP5==0, NA,  EARNIMP5))

miss_var_summary(missingness_test_set2)


lapply(missingness_test_set, function(col) {
  round(100 * prop.table(table(col)), 2)  
})


```

```{r}
data%>%
  count(Race)

```


```{r, categorizing household income}

data<-data%>%
  mutate(Family_Earnings_Nonimputed=case_when(
    INCFAM97ON2%in%c(10)~"Low Household Income (<$35k)",
    INCFAM97ON2%in%c(20,30,21)~"Middle Household Income ($35k-$100k)",
    INCFAM97ON2%in%c(32)~"High Household Income $100k+",
    INCFAM97ON2==96~"Above $20k but otherwise unknown",
    INCFAM97ON2%in%c(97,98,99)~"Unknown"
  ))

table(data$Family_Earnings_Nonimputed)

```


STARTING ANALYSIS
```{r}

data_analysis_omit<-data%>%
    select(exposure_birth, Mort_recode, Race, AGE, sex, Diabetes_Lifetime_Race, Diabetes_Lifetime, BMI_R_Cat, Education_recode, Earnings_recode, Smoking_recode, Insurance_Status, USBorn_Recode, PERWEIGHT, PSU, STRATA, MORTUCODLD, Family_Earnings_Nonimputed)%>%
  mutate(study_exposure=exposure_birth-AGE)%>%
  filter(!study_exposure==0)


data_analysis_diabetes<-data_analysis_omit%>%
  #filter(Diabetes_Lifetime=="Non-Diabetic")%>%
  filter(Diabetes_Lifetime=="Diabetic")


data_weighted<-survey::svydesign(id=~PSU,
          weights=~PERWEIGHT,
          #strata=~STRATA,
          nest=TRUE,
          survey.lonely.psu="adjust",
          data=data_analysis_diabetes)

cox_weighted_diabetes<-svycoxph(Surv(study_exposure, Mort_recode==TRUE) ~ Race + AGE+ sex+ Education_recode+Family_Earnings_Nonimputed+Smoking_recode+Insurance_Status+BMI_R_Cat, design = data_weighted)#Remove foreign born and asians lower risk


summary(cox_weighted_diabetes)#not including nativity with new family earnings


cox_weighted_diabetes<-svycoxph(Surv(study_exposure, Mort_recode==TRUE) ~ Race + AGE+ sex+ Education_recode+Earnings_recode+Smoking_recode+Insurance_Status+BMI_R_Cat, design = data_weighted)#Remove foreign born and asians lower risk


summary(cox_weighted_diabetes)
summary(cox_weighted_diabetes_w_nativity)#not including nativity, original analysis

```