---
title: "BenSzetoPostWeek6Analysis"
author: "Ben Szeto"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, loading libraries}
library(tidyverse)
library(knitr)
library(plotly)
library(ggeffects)
library(ggformula)
library(ipumsr)
library(cmprsk)
```


```{r}


ddi <- read_ipums_ddi("/Users/benszeto/Library/CloudStorage/Box-Box/CARE Scholars 2024 - Diabetes Mortality Project/Data and Code/nhis_00029.xml")

data1 <- read_ipums_micro(ddi)

ddi <- read_ipums_ddi("/Users/benszeto/Library/CloudStorage/Box-Box/CARE Scholars 2024 - Diabetes Mortality Project/Data and Code/nhis_00027.xml")

data2 <- read_ipums_micro(ddi)

ddi <- read_ipums_ddi("/Users/benszeto/Library/CloudStorage/Box-Box/CARE Scholars 2024 - Diabetes Mortality Project/Data and Code/nhis_00030.xml")

data3 <- read_ipums_micro(ddi)

```

```{r, data merging}
data1<-data1%>%#Selecting variables of interest from data1
  select(NHISPID, DIABETICAGE, DIAYRSAGO)

data3<-data3%>%#Selecting variables of interest from data3
  select(NHISPID, MORTDODY, MORTWT, MORTSTAT)

data<-merge(data1, data2, by="NHISPID")
data
data<-merge(data, data3, by="NHISPID")

```
```{r}
data%>%
  filter(!MORTDODY==9999)%>%
  select(MORTDODY)%>%
  arrange(desc(MORTDODY))

```

```{r, defining exposure time since DOB}
data<-data%>%
  mutate(exposure_birth=ifelse(
    MORTSTAT==1,
    MORTDODY-YEAR+AGE,#If dead, time ends at year of death
    2019-YEAR+AGE#If alive or NIU, time ends at 2019
    ))

```

```{r, defining exposure time since Diabetes Diagnosis}

data<-data%>%
  mutate(exposure_diabetes=ifelse(
    !DIABETICAGE==96 & !MORTDODY==9999,
    (AGE-DIABETICAGE)+(MORTDODY-YEAR),
    NA
  ))

```

```{r, data cleaning}
data<-data%>%
  mutate(racea=as_factor(RACEA))%>%
  mutate(mortstat=as_factor(MORTSTAT))%>%
  mutate(morthypr=MORTHYPR)%>%
  filter(racea%in%c("Chinese", "Asian Indian", "White", "Filipino"))%>% #selecting Chinese, Asian Indian, Filipino, and White
  filter(!BMI==0)%>% #filtering out extranious BMIs
  filter(BMI<90)%>%
  filter(MORTELIG==1)%>%
  mutate(BMI_R_Cat=ifelse(racea=="White", 
                          case_when(BMI<18.5~"Underweight",#BMI thresholds for Whites
                                    BMI>=18.5 & BMI<25~"Normal Weight",
                                    BMI>=25 & BMI <30~"Overweight",
                                    BMI>=30~"Obese"),
                          case_when(BMI<18.5~"Underweight",#BMI thresholds for Asians (Considered all races not White)
                                    BMI>=18.5 & BMI<23~"Normal Weight",
                                    BMI>=23 & BMI <27.5~"Overweight",
                                    BMI>=27.5~"Obese")))%>%#27.5 is obese for Asians
mutate(CVD_MOR=ifelse(MORTUCODLD%in%c(1, 5), TRUE, FALSE))
```
#3 possible routes
# Among diabetics, how many die from cvd (look into people w and w/o diabetes) $just look at diabetes, not whether diabetes related. 
#Among races, how many die from diabetes related cvd
# Among people with diabetes, how long you have diabetes, how does that impact cvd mort. (likely issue w sample size)


Model 1: Among diabetics, how many die from cvd (look into people w and w/o diabetes) $just look at diabetes, not whether diabetes related
```{r}
data_mod1<-data%>%
  mutate(Diabetes_Lifetime=case_when(
    DIABETICEV==2|MORTDIAB==2~"Diabetic",
    DIABETICEV%in%c(0,7,8,9) & MORTDIAB==9~"Unknown/Not in Universe",
    TRUE~"Non-Diabetic"
  ))%>%
  mutate(CVDMORT_Diabetes=ifelse(CVD_MOR==TRUE&Diabetes_Lifetime=="Diabetic", TRUE, FALSE))%>%#Whether individual has diabetes and dies from Heart Attack or Stroke
  filter(MORTELIG==1)

```

```{r}
data_mod1%>%
  group_by(CVDMORT_Diabetes, racea)%>%
  summarize(
    n(),
    mean(exposure_birth)
  )%>%
  arrange(desc(racea))

```

```{r, competing risk analysis model 1, exposure time since birth, endpoint is CVD death with diabetes}

 cuminc_test<-cuminc(ftime=data_mod1$exposure_birth,fstatus=data_mod1$CVDMORT_Diabetes, group=data_mod1$racea)
 cuminc_test
 plot(cuminc_test, col = c("black", "blue", "green", "red"), lty=1, ylim=c(0,0.5))

```




Model 2: Among races, how many die from diabetes related cvd


```{r}

unique(data$MORTDIAB)
unique(data$MORTUCODLD)

data_mod2<-data%>%
  mutate(Diabetes_CVD=ifelse(
    MORTDIAB==2 & MORTUCODLD %in%c(1,5),
    TRUE,
    FALSE
  ))

data_mod2%>%
  group_by(Diabetes_CVD, racea)%>%
  summarize(
    n(),
    mean(exposure_birth)
    )%>%
  arrange(desc(racea))
  

```

```{r competing risk analysis exposure time since birth, }
 cuminc_test<-cuminc(ftime=data_mod2$exposure_birth,fstatus=data_mod2$Diabetes_CVD, group=data_mod2$racea)
 cuminc_test
 plot(cuminc_test, col = c("black", "blue", "green", "red"), lty=1, ylim=c(0,0.2))

```




Model 3: Among people with diabetes, how long you have diabetes, how does that impact cvd mort. (likely issue w sample size)

```{r}

data%>%
  filter(!is.na(exposure_diabetes))%>%
  group_by(racea)%>%
  count()

```